Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-09-04 manuscripts/manuscript1.qmd
making more functions

table_2 <- with_dir(here(), tar_read(table_2_aggressive))
tibble_2 <- as_tibble(table_2) |> select(-1)

@@

tibble_2 <- bind_cols(column_names, tibble_2) |>
  rename(
    "Right Hemisphere" = "**Right**, N = 1,757",
    "Left Hemisphere" = "**Left**, N = 1,720",
    "Outcome" = ...1
  ) |>
  full_join(table_almost_2, by = "Outcome") |>
  gt()

@@

predictions(models$"Neurosurgical Intervention", by = "ich_laterality") |>
  posterior_draws() |>
  ggplot(aes(x = draw, fill = ich_laterality)) +
  geom_density(alpha = .7) +
  scale_fill_manual(values = c("#054224", "#ff8800")) +
  scale_y_continuous(
    limits = c(0, 100)
  ) +
  scale_x_continuous(
    limits = c(0, 0.14),
    breaks = seq(0, 0.14, 0.02),
    labels = scales::percent
  ) +
  labs(
    title = "Predicted Probability",
    fill = "ICH Laterality",
    y = NULL
  ) +
  theme_ich()

```{r figure 2}
#| echo: false
#| label: figure 2
#| fig-width: 10

>>>>

table_2 <- with_dir(here(), tar_read(table_2_aggressive))

tibble_2 <- table_2[[1]] |>
  select(c(label, stat_1, stat_2))

@@

tibble_2 <- tibble_2 |>
  rename(
    "Left Hemisphere" = "stat_1",
    "Right Hemisphere" = "stat_2",
    "Outcome" = "label"
  ) |>
  full_join(table_almost_2, by = "Outcome") |>
  gt()

@@
